Introducing the \NAME Framework\\ for Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-15 paper.tex
setup code generator and semantic model

@@

@@

- semantic model \cite{fowler2010domain}
- model transformations
- code model + syntactic mapping using coding pattern-like instructions

>>>>

\usepackage{tikz}

@@

To convert the DSL based ID algorithms into production-ready code, we propose
the use of a code generator. Although many approaches here are applicable, like
template based text expansion, XSLT transformations or even using the
CodeDom\cite{dollard2004code}, we believe that for the level of functional
transformations that need to be performed, a richer model is required.

A semantic model \cite{fowler2010domain}, tied closely to the DSL itself, can
fulfil this role. Semantic transformations can now be applied to create a
code-oriented model, comparable to the idea of CodeDom. From there on,
syntactic transformations an emit actual source code. Figure
\ref{fig:code-generation} shows the overall procedure.

\begin{figure}[H]
\begin{tikzpicture}[
    nonterminal/.style={
% The shape:
rectangle,
% The size:
      minimum size=6mm,
% The border:
      very thick,
      draw=red!50!black!50,
      % The filling:
top color=white,
bottom color=red!50!black!20, % and something else at the bottom % Font
font=\itshape
    }]
  \node [nonterminal] {TODO};
\end{tikzpicture}
\caption{Overview code generation process}
\label{fig:code-generation}
\end{figure}

\subsection{Semantic Model}

@@

Figure \ref{fig:meta-model} shows the meta-model of the the semantic model.

\begin{figure}[H]
\begin{tikzpicture}[
    nonterminal/.style={
% The shape:
rectangle,
% The size:
      minimum size=6mm,
% The border:
      very thick,
      draw=red!50!black!50,
      % The filling:
top color=white,
bottom color=red!50!black!20, % and something else at the bottom % Font
font=\itshape
    }]
  \node [nonterminal] {TODO};
\end{tikzpicture}
\caption{Semantic Model Meta-Model}
\label{fig:meta-model}
\end{figure}
